%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Paul W.}{Hacker}

\position{Postdoctoral Fellow}
\address{University of British Columbia}

\email{\href{mailto:paul.w.hacker@gmail.com}{\nolinkurl{paul.w.hacker@gmail.com}}}
\orcid{0000-0001-9786-3715}
\github{paulwhacker}
\linkedin{paul-w-hacker}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {May 2023}
    {Paul W. Hacker~~~·~~~CV}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{PhD Microbiology \& Immunology}{Stanford University}{Stanford, CA}{2022}{\begin{cvitems}
\item Dissertation - Malaria susceptibility: genetic factors and immune adaptation during pregnancy
\end{cvitems}}
    \cventry{BSc Molecular Microbiology \& Immunology with Minors in Mathematics \& Chemistry}{University of Nevada, Reno}{Reno, NV}{2017}{\begin{cvitems}
\item Honors Thesis - In vivo distribution and clearance of purified capsular polysaccharide from Burkholderia pseudomallei in a Murine Model
\end{cvitems}}
\end{cventries}

\hypertarget{research}{%
\section{Research}\label{research}}

\begin{cventries}
    \cventry{Jagannathan Lab - Department of Medicine }{Graduate Student Researcher}{Stanford University}{October 2020 - Present }{\begin{cvitems}
\item Investigate cellular correlates for acquired immunity against placental malaria in pregnant mothers from Uganda. \begin{itemize}
        \item Culture VAR2CSA expressing \emph{Plasmodium falciparum}.
        \item Fluorescent activated cell-sorting and bulk RNA sequencing.
        \item Flow cytometry and analysis of large datasets.
    \end{itemize}
\end{cvitems}}
    \cventry{Schneider Lab - Department of Microbiology \& Immunology}{Graduate Student Researcher}{Stanford University}{July 2018 - September 2020}{\begin{cvitems}
\item Identify new genetic loci associated with resistance to malaria infection in a \emph{Plasmodium chabaudi} diversity outbred model. \begin{itemize}
        \item Genetic loci mapping with multiparent populations with qtl2 package.
        \item Handle Mice using \emph{Plasmodium chabaudi} infection model.
    \end{itemize}
\end{cvitems}}
    \cventry{Hurtado Group - Department of Mathematics \& Statistics}{Undergraduate Researcher}{University of Nevada, Reno}{October 2016 - August 2018}{\begin{cvitems}
\item Generalized the linear chain trick using properties of erlang distributions to translate stochastic integrodifferential equations into simpler ordinary differential equations for modelers.
\end{cvitems}}
    \cventry{AuCoin Lab - Department of Microbiology \& Immunology}{Undergraduate Researcher}{University of Nevada, Reno}{February 2014 - May 2017}{\begin{cvitems}
\item Verified \emph{Burkholderia pseudomallei} capsular polysaccharide as a viable biomarker in a murine model. Cultured Leptospirosis interrogans. Subclass switched antibodies decrease limit of detection of a lateral flow immunoassay. \begin{itemize}
        \item Culturing Hybridoma cell lines in bioreactors for antibodies.
        \item Measuring clearance kinetics of capsular polysaccharide.
        \item Optimized Ig subclass for lateral flow immunoassay using ELISAs.
    \end{itemize}
\end{cvitems}}
\end{cventries}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\begin{cventries}
    \cventry{Hume Center for Writing and Speaking}{\href{https://undergrad.stanford.edu/people/adam-kirosingh}{\color{black}{Graduate Writing Tutor}}}{Stanford University}{June 2020 - Present }{\begin{cvitems}
\item Tutor undergraduates and graduate students virtualy one-on-one at all stages of the writing process ranging from scholarship applications to written class assignments.
   \begin{itemize}
     \item \href{https://github.com/akirosingh/CV/blob/de14a69ecccf4760587b2f92245a23c48535b227/docs/winter_2021_feedback.pdf}{\color{black}{Winter 2021 Testimonials}} - I most appreciated his enthusiasm and encouraging attitude, since it made me less nervous about sharing my writing and getting feedback on it!
     \item \href{https://github.com/akirosingh/CV/blob/43bc8932180c69404f7dfa6d5604b4c1133f24e8/docs/fall_2020_feedback.pdf}{\color{black}{Fall 2020 Testimonials}} - Adam made the session really comfortable and low stress which helped me get through the material and feel comfortable asking questions!
   \end{itemize}
\end{cvitems}}
    \cventry{Microbial Pathogenesis}{Teaching Assistant}{Remote Learning}{April 2020 - June 2020}{\begin{cvitems}
\item Held weekly office hours, guest lectured, developed and graded research proposals
\end{cvitems}}
\end{cventries}

\hypertarget{leadership}{%
\section{Leadership}\label{leadership}}

\begin{cventries}
    \cventry{Karuna Initiative}{Data Analyst}{Tormabum, Sierra Leone}{June 2019 - September 2019}{\begin{cvitems}
\item Lead community reports for summer pilot  \begin{itemize}
        \item Summarize timeseries data of 60 students wellbeing.
        \item Identify trends in community responses to advise graduate student policy.
    \end{itemize}
\end{cvitems}}
    \cventry{WARC}{Social Entrepeneurship Team Member}{Tormabum, Sierra Leone}{July 2019 - September 2019}{\begin{cvitems}
\item Establishing a low-cost drying machine in rural Sierra Leone for subsistence farmers. \begin{itemize}
        \item Prototyping, testing and manufacturing a half-ton scale maize-drying machine.
        \item Partnering with WARC (West African Rice Company) and FINIC Industries to build and implement maize dryer.
    \end{itemize}
\end{cvitems}}
    \cventry{Noora Health}{\href{https://extreme.stanford.edu/projects/skincubated/}{\color{black}{Design Consultant}}}{Bangalore, India}{February 2019 - June 2019}{\begin{cvitems}
\item Designed a newborn \href{https://extreme.stanford.edu/projects/skincubated/}{\color{black}{health education kit}} to encourage kangaroo care in mothers of low birthweight babies in India. \begin{itemize}
        \item Prototyping education material using Adobe Illustrator.
        \item User-testing with new mothers in hospitals and home visits.
    \end{itemize}
\end{cvitems}}
\end{cventries}

\hypertarget{relevant-courses}{%
\section{Relevant Courses}\label{relevant-courses}}

\begin{cventries}
    \cventry{Stanford University}{}{}{}{\begin{cvitems}
\item BIOS 221: Modern Statistics for Modern Biology
\item CME 193: Introduction to Scientific Python
\end{cvitems}}
    \cventry{University of Nevada, Reno}{}{}{}{\begin{cvitems}
\item MATH 420: Mathmatical Modeling
\item MATH 461: Probability Theory
\item MATH 462: Introduction to Stochastic Processes
\item STAT 467: Statistical Theory
\end{cvitems}}
\end{cventries}

\hypertarget{technical-skills}{%
\section{Technical Skills}\label{technical-skills}}

\begin{table}[!h]
\centering\begingroup\fontsize{9}{11}\selectfont

\begin{tabular}{>{\centering\arraybackslash}p{4.75cm}>{\centering\arraybackslash}p{4.75cm}>{\centering\arraybackslash}p{4.75cm}}
\toprule
\textcolor[HTML]{414141}{\textbf{Coding Languages}} & \textcolor[HTML]{414141}{\textbf{Software}} & \textcolor[HTML]{414141}{\textbf{Markup Languages}}\\
\midrule
\textcolor[HTML]{7f7f7f}{R, Python, Mathematica, MATLAB} & \textcolor[HTML]{7f7f7f}{GIT, SLURM, High-Performance Computing} & \textcolor[HTML]{7f7f7f}{CSS, HTML, \LaTeX, RMarkdown, Bootstrap}\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

\hypertarget{honors}{%
\section{Honors}\label{honors}}

\begin{cventries}
    \cventry{NIH training program for Stanford Bioscience PhD Students}{Cellular Molecular Biology Trainee}{Stanford, CA}{2019}{}\vspace{-4.0mm}
    \cventry{Granted to Honors students with exceptional theses}{Honors Undergraduate Research Award}{University of Nevada, Reno}{2016}{\begin{cvitems}
\item Honors Thesis: In vivo distribution of B. pseudomallei capsular polysaccharide
\end{cvitems}}
    \cventry{Awarded by SACNAS to less than 5\% of poster presenters at annual conference}{Poster Award for SACNAS Diversity Conference}{Long Beach, CA}{2016}{\begin{cvitems}
\item Poster: Probability distributions of system average interruption frequency index
\end{cvitems}}
    \cventry{Awarded for excellent applications to the goldwater scholarship}{Barry M. Goldwater Scholarship Honorable Mention}{Saint Peter, MN}{2016}{\begin{cvitems}
\item Proposal on Immunoglobulin G Subclass Switching Impacts Sensitivity of an Immunoassay Targeting Francisella Tularensis Lipopolysaccharide
\end{cvitems}}
    \cventry{Given to undergraduate students with promising research proposals}{Nevada Undergraduate Research Award}{University of Nevada, Reno}{2014}{\begin{cvitems}
\item Awarded 3 consecutive years
\end{cvitems}}
    \cventry{Competitive national fellowship for research in Microbiology }{American Society for Microbiology Undergraduate Research Fellow}{Washington, DC}{2016}{\begin{cvitems}
\item Led to a poster presentation at ASM Microbe 2017
\end{cvitems}}
    \cventry{Funding for undergraduate research in biosciences}{Nevada INBRE Undergraduate Research Opportunity Program}{University of Nevada, Reno}{2015}{}\vspace{-4.0mm}
    \cventry{Scholars program for first-generation college students pursuing higher education}{Ronald E. McNair Post-Baccalaureate Achievement Program Scholar}{University of Nevada, Reno}{2014}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\begin{itemize}
\item
  \textbf{Kirosingh, A.S.}, De La Parte, L., Ty, M., Kakuru, A.,
  Muhindo, M. K., Thulin, N., Kamya, M., Feeney, M., Dorsey, G., Wang,
  T.T., Jagannathan P., Cellular correlates for protection against
  malaria acquired across multiple pregnancies (manuscript in
  preparation)
\item
  \textbf{Kirosingh, A.S.}, Gupta, A.S., Chevee, V., Davis, N., Cumnock,
  K., Lissner, M., Schneider, D.S. Malaria Susceptibility Loci
  Identified in the Diversity Outbred Mouse Population (manuscript in
  preparation)
\item
  Hurtado, P.J., \textbf{Kirosingh, A.S.}, 2019. Generalizations of the
  `Linear Chain Trick': incorporating more flexible dwell time
  distributions into mean field ODE models. J. Math. Biol. 79,
  1831--1883. \url{https://doi.org/10.1007/s00285-019-01412-w}
\item
  Nualnoi, T., \textbf{Kirosingh, A.}, Pandit, S.G., Thorkildson, P.,
  Brett, P.J., Burtnick, M.N., AuCoin, D.P., 2016. In vivo Distribution
  and Clearance of Purified Capsular Polysaccharide from Burkholderia
  pseudomallei in a Murine Model. PLOS Neglected Tropical Diseases 10,
  e0005217. \url{https://doi.org/10.1371/journal.pntd.0005217}
\item
  Nualnoi, T., \textbf{Kirosingh, A.}, Basallo, K., Hau, D.,
  Gates-Hollingsworth, M.A., Thorkildson, P., Crump, R.B., Reed, D.E.,
  Pandit, S., AuCoin, D.P., 2018. Immunoglobulin G subclass switching
  impacts sensitivity of an immunoassay targeting Francisella tularensis
  lipopolysaccharide. PLOS ONE 13, e0195308.
  \url{https://doi.org/10.1371/journal.pone.0195308}
\end{itemize}

\hypertarget{published-abstracts}{%
\subsection{Published Abstracts}\label{published-abstracts}}

\begin{itemize}
\item
  Hurtado, P., \textbf{Kirosingh, A.}, 2018. The Generalized Linear
  Chain Trick: A new tool to build ODE models with more flexible
  dwell-time distributions. Presented at the 2018 ESA Annual Meeting
  (August 5 -- 10), ESA.
\item
  \textbf{Kirosingh, A.}, 2017. PROBABILITY DISTRIBUTIONS OF SYSTEM
  AVERAGE INTERRUPTION FREQUENCY INDEX. Presented at the 2017 AAAS
  Annual Meeting (February 16-20, 2017), AAAS.
\end{itemize}



\end{document}
